Universal relations after GW170817\kc{Here and elsewhere: I suggest we use the term "EoS-insensitive" instead of "universal" relations}

### 2019-01-02 paper/bin-love-after-gw170817.tex
added C-Love section to paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
% Intro
The thermodynamic relationship between pressure and density (the equation of state) of \kc{cold} supranuclear matter, accessible primarily in neutron stars\kc{this statement makes nuclear experiment people not happy}, is critical to the study of such stars, and is one of the largest uncertainties in nuclear physics to date. 
% How to probe
The extraction of tidal deformabilities from the gravitational waveforms of binary neutron star merger events, such as GW170817, is a promising method of probing the nuclear structure.
% What was done before - Binary Love
Previous studies have shown that approximately equation of state insensitive ``binary Love universal relations" exist between symmetric and antisymmetric combinations of individual tidal deformabilities, which are difficult to be independently measured with second-generation gravitational wave interferometers.
% What was done before - I-Love-Q
Similarly, another set of equation of state \sout{independent}\kc{insensitive} relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), and quadrupole moment (Q) - known as the ``I-Love-Q universal relations."
% What universal relations do
Such universal relations\kc{so far we have said "EoS-insensitive", "EoS-independent", and "universal". We should pick a name and stick with it. I suggest "EoS-insensitive"} allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing the uncertainty of the dominant tidal effect in parameter estimation\kc{You mean $\tilde{\Lambda}$? In our paper with Carl and Aaron we showed that the binary Love relation doesn't affect the $\tilde{\Lambda}$ measurement much.}.
% What we will do
\kc{Add a sentence saying that even the more precise relations have some EoS variation which can cause a systematic error which can be marginalized over}
In this document, we explain how one can reduce equation of state variation for both binary Love and I-Love-Q universal relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers\kc{but we show that the systematic effects of these relations is very small until next-G detectors.}. 
We achieve this  by restricting to only equations of state drawn from the 90\% posterior constraint on pressure as a function of density, as derived by the LIGO Collaboration.
% What we found
We find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with a mass ratio of 0.75, and in I-Love-Q universality by factors of $\sim 50$\%.
% Conclude
We end by comparing systematic errors on tidal measurement due to the equation of state variation with statistical errors and comment on whether one can safely use these universal relations with future gravitational wave observations.\kc{We should give the answer to this here: Yes!}
\end{abstract}

@@

%Universal relations
Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\tilde{\Lambda}$, known as the chirp deformability\kc{That's the first time I hear this term!}.
Previous work by Yagi and Yunes~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love universal relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction on the removal of one parameter from the model\kc{decrease in uncertainty in which parameter?}, and (ii) the ability to measure the secondary tidal parameter upon measurement of the first~\cite{Katerina:residuals}.  
Use of this relations leads to up to an order of magnitude improvement in parameter estimation \kc{of what?} through a simple Fisher analysis~\cite{Yagi:binLove}, also confirmed with the detailed analysis of~\cite{Katerina:residuals}.
Similar ``I-Love-Q" universal relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, and tidal deformability; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.

@@

%What we did
In this paper we attempt to improve binary Love and I-Love-Q universal relations by imposing constraints on the EoS found by GW170817~\cite{LIGO:posterior,TheLIGOScientific:2017qsa}.
First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must be drawn from GW170817s 90\% credible posterior in pressure as a function of density, and (ii) don't impose any restrictions for comparison purposes.
Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
In addition, we determine the degree to which hybrid star EoSs obey binary Love universal relations.
Finally, through a simple Fisher analysis, we consider the value in improving universal relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in universal relations.

%Final Results
Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
Unfortunately\kc{??}, due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the universal relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2, aLIGO, a\texttt{++}, Voyager, ET, CE$)$\zc{cite these individually}\kc{a\texttt{++} should be A\texttt{+}}.
Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$)\kc{How are we combining the uncertainty on $\tilde{\Lambda}$ when each event will have a different $\tilde{\Lambda}$?}.
These values are further tabulated in Table~\ref{tab:variances}.
It can be seen from this figure that the statistical errors from parameter extraction become comparable the universal relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love universal relations will become viable\kc{viable? you mean necessary?}.
\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{stackedFisher.eps}
\end{center}
\caption{
Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if observed with future interferometers aLIGO, a++, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
This is compared to the combined uncertainty $\sigma^A_N$ (red) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper (teal), central (orange), and lower (magenta) limits of expected binary NS merger detection rates for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observation year \kc{Instead of points, it might be clearer to show this with shaded regions from the upper to the lower rate.}.
It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (purple shaded region) for Voyager and on.
Note there is no simulated populations of events under the O2 design sensitivity - due to there only being a single event during the observing period.
These results are further tabulated in Table~\ref{tab:variances}.
}
\label{fig:stackedFisher}
\end{figure}

%outline
The organization of this paper is outlined below.
We begin with a complementary background and theory material in Sec.~\ref{sec:theory}.
We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love and I-Love-Q universal relations, and considering how well hybrid star EoSs agree with the universal relations.
We next examine these improved universal relations and question whether or not they are useful for future interferometers in Sec.~\ref{sec:observations}.
We conclude in Sec.~\ref{sec:conclusion} by discussing our results and mentioning avenues of future work.
Throughout this paper, we have adopted geometric units of $G=c=1$, unless otherwise stated.

@@

Similar universal relations have been found to exist between individual NS observables: moment of inertia (I), tidal deformability (Love), and quadrupole moment (Q), known as the ``I-Love-Q" universal relations~\cite{Yagi:ILQ}.
These have been found to be EoS insensitive by up to 1\% for each of pair of observables.
In this paper, we show improvement in both of these universal relations by restricting to EoSs sampled from GW170817s posterior on pressure as a function of density.
%%%%%%%%%%%%%%%%%%%%%%%%% Begin universal relations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Universal relations}\label{sec:universal}
In this section, we follow the analyses performed in~\cite{Yagi:binLove,Yagi:ILQ} with two new sets of 100 spectrally generated EoS: (i) posterior samples randomly selected from GW170817s 90\% posterior on on pressure as a function of density as shown in the left panel of Fig.~\ref{fig:eos}, and (ii) those unconstrained by any prior EoS information, as shown in the right panel of Fig.~\ref{fig:eos}.\kc{only one panel}

@@

\begin{table}
\centering
\caption{
Comparison between the universal relations (both I-Love-Q and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here. 
The maximum EoS variation, given by the largest fractional difference from the fits as shown in Figs.~\ref{fig:ILQ} and~\ref{fig:binLove}, sees a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as previous works.
Additionally, notice how the maximal EoS variation for the unconstrained set of EoSs is slightly higher than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.
}\label{tab:maxVar}
\begin{tabular}{ c  || c c c } 
 \hline
 \hline
 \textbf{Universal} & \multicolumn{3}{c}{\textbf{Maximal EoS Variability}} \\
 \cline{2-4}
 \textbf{Relation} & \multicolumn{1}{c|}{\emph{Previous}} & \multicolumn{1}{c|}{\emph{Unconstrained}} & \emph{Constrained}\\
 \hline
 $\bar{I}-\Lambda$ &  $0.0059$ & $0.0076725$ & $0.0031383$\\
 $\bar{Q}-\Lambda$ & $0.0010$ & $0.012617$ & $0.0046612$\\
 $\bar{I}-\bar{Q}$ & $0.012$ & $0.014895$ & $0.0057157$\\
 \hline
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.50$} & \multirow{2}{*}{$0.5723891$} & \multirow{2}{*}{$0.2140192$}\\
 $(q=0.90)$ & & &\\
 \cline{1-1}
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.20$} & \multirow{2}{*}{$0.2447418$} & \multirow{2}{*}{$0.0828446$}\\
  $(q=0.7)$ & & &\\
  \cline{1-1}
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.025$} & \multirow{2}{*}{$0.0384088$} & \multirow{2}{*}{$0.0182308$}\\
  $(q=0.50)$ & & &\\
  \cline{1-1}
\hline
\hline
\end{tabular}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%% Begin Discussion %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Discussion}\label{sec:conclusion}
The recent GW observation of binary NS merger GW170817 placed constraints on the supranuclear matter EoS for NSs.
We take advantage of this by generating a restricted set of spectral EoSs which agree with this observation to reduce uncertainties upon the extraction of tidal parameters from future GW events.
Important previous work by Yagi and Yunes~\cite{Yagi:ILQ,Yagi:binLove} found EoS-insensitive universal relations between symmetric and antisymmetric combinations of NS tidal deformabilities, which aid in the extraction of said tidal parameters.
We find an improvement upon these universal relations by a factor of $\sim 59$\% for stars with mass ratios of $0.75$ by restricting to the EoS posterior samples from GW170817s 90\% credible region on pressure as a function of density.
Similarly, we find an increase in I-Love-Q universality by a factors of $\sim 50$\%.
In addition, we find that binaries consisting of one massive hybrid quark-hadron star, and one small-mass hadron star do not obey these universal relations -- explained by the large difference in $\tilde{\Lambda}$ displayed between the constituent stars.
To improve on this, we construct new ``hybrid matter binary Love relations", applied to only the hybrid branches of the transitional EoSs.
This results in EoS variability similar to that found for the nuclear matter fits.
Further, we analyze the impact of this improvement for future binary NS merger detections, as the current detector sensitivity is not yet small enough to accurately constrain $\tilde{\Lambda}$ enough for universal relations to make a difference.
We find that future interferometers Voyager, CE, and ET-D all experience statistical uncertainties upon the extraction of $\tilde{\Lambda}$ small enough to become comparable to the systematic errors injected through the use of improved universal relations (found to be $12.014$), as depicted in Fig.~\ref{fig:stackedFisher} and Table~\ref{tab:variances}.
Finally, in Appendix~\ref{app:measurement} we investigate the effect of NS binary mass ratio q on the measurement accuracy of $\tilde\Lambda$.
We find that second generation interferometers lose accuracy as one increases the mass ratio, while third generation detectors observe a large increase of accuracy due to the correlations between $\tilde\Lambda$ and $\delta\tilde\Lambda$.
This indicates that the use and further improvement of universal relations is justified for future GW observations of binary NS merger events.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
% Intro
The thermodynamic relationship between pressure and density (the equation of state) of \kc{cold} supranuclear matter, accessible primarily in neutron stars\kc{this statement makes nuclear experiment people not happy}, is critical to the study of such stars, and is one of the largest uncertainties in nuclear physics to date. 
% How to probe
The extraction of tidal deformabilities from the gravitational waveforms of binary neutron star merger events, such as GW170817, is a promising method of probing the nuclear structure.
% What was done before - Binary Love
Previous studies have shown that approximately equation of state insensitive ``binary Love universal relations" exist between symmetric and antisymmetric combinations of individual tidal deformabilities, which are difficult to be independently measured with second-generation gravitational wave interferometers.
% What was done before - I-Love-Q
Similarly, another set of equation of state independent relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), quadrupole moment (Q), and compactness (C) - known as the ``I-Love-Q" and ``C-Love" universal relations.
% What universal relations do
Such universal relations\kc{so far we have said "EoS-insensitive", "EoS-independent", and "universal". We should pick a name and stick with it. I suggest "EoS-insensitive"} allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing the uncertainty of the dominant tidal effect in parameter estimation\kc{You mean $\tilde{\Lambda}$? In our paper with Carl and Aaron we showed that the binary Love relation doesn't affect the $\tilde{\Lambda}$ measurement much.}.
% What we will do
\kc{Add a sentence saying that even the more precise relations have some EoS variation which can cause a systematic error which can be marginalized over}
In this document, we explain how one can reduce equation of state variation for both binary Love and I-Love-Q universal relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers\kc{but we show that the systematic effects of these relations is very small until next-G detectors.}. 
We achieve this  by restricting to only equations of state drawn from the 90\% posterior constraint on pressure as a function of density, as derived by the LIGO Collaboration.
% What we found
We find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with a mass ratio of 0.75, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim 50$\%.
% Conclude
We end by comparing systematic errors on tidal measurement due to the equation of state variation with statistical errors and comment on whether one can safely use these universal relations with future gravitational wave observations.\kc{We should give the answer to this here: Yes!}
\end{abstract}

@@

%Universal relations
Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\tilde{\Lambda}$, known as the chirp deformability\kc{That's the first time I hear this term!}.
Previous work by Yagi and Yunes~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love universal relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction on the removal of one parameter from the model\kc{decrease in uncertainty in which parameter?}, and (ii) the ability to measure the secondary tidal parameter upon measurement of the first~\cite{Katerina:residuals}.  
Use of this relations leads to up to an order of magnitude improvement in parameter estimation \kc{of what?} through a simple Fisher analysis~\cite{Yagi:binLove}, also confirmed with the detailed analysis of~\cite{Katerina:residuals}.
Similar ``I-Love-Q" and ``C-Love" universal relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, tidal deformability, and compactness; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.

@@

%What we did
In this paper we attempt to improve binary Love and I-Love-Q universal relations by imposing constraints on the EoS found by GW170817~\cite{LIGO:posterior,TheLIGOScientific:2017qsa}.
First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must be drawn from GW170817s 90\% credible posterior in pressure as a function of density, and (ii) don't impose any restrictions for comparison purposes.
Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality (binary Love, I-Love-Q, and C-Love) from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
In addition, we determine the degree to which hybrid star EoSs obey binary Love universal relations.
Finally, through a simple Fisher analysis, we consider the value in improving universal relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in universal relations.

%Final Results
Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
Additionally, we find that hybrid quark-hadron stars do obey the I-Love-Q and C-Love universal relations, with sightly increased EoS variability.
We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
Unfortunately\kc{??}, due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the universal relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2, aLIGO, a\texttt{++}, Voyager, ET, CE$)$\zc{cite these individually}\kc{a\texttt{++} should be A\texttt{+}}.
Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$)\kc{How are we combining the uncertainty on $\tilde{\Lambda}$ when each event will have a different $\tilde{\Lambda}$?}.
These values are further tabulated in Table~\ref{tab:variances}.
It can be seen from this figure that the statistical errors from parameter extraction become comparable the universal relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love universal relations will become viable\kc{viable? you mean necessary?}.
\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{stackedFisher.eps}
\end{center}
\caption{
Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if observed with future interferometers aLIGO, a++, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
This is compared to the combined uncertainty $\sigma^A_N$ (red) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper (teal), central (orange), and lower (magenta) limits of expected binary NS merger detection rates for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observation year \kc{Instead of points, it might be clearer to show this with shaded regions from the upper to the lower rate.}.
It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (purple shaded region) for Voyager and on.
Note there is no simulated populations of events under the O2 design sensitivity - due to there only being a single event during the observing period.
These results are further tabulated in Table~\ref{tab:variances}.
}
\label{fig:stackedFisher}
\end{figure}

%outline
The organization of this paper is outlined below.
We begin with a complementary background and theory material in Sec.~\ref{sec:theory}.
We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love, I-Love-Q, and C-Love universal relations, and considering how well hybrid star EoSs agree with the universal relations.
We next examine these improved universal relations and question whether or not they are useful for future interferometers in Sec.~\ref{sec:observations}.
We conclude in Sec.~\ref{sec:conclusion} by discussing our results and mentioning avenues of future work.
Throughout this paper, we have adopted geometric units of $G=c=1$, unless otherwise stated.

@@

Similar universal relations have been found to exist between individual NS observables: moment of inertia (I), tidal deformability (Love), quadrupole moment (Q), and compactness (C), known as the ``I-Love-Q" and ``C-Love" universal relations~\cite{Yagi:ILQ, Yagi:binLove}.
These have been found to be EoS insensitive by up to 1\% and 6.5\% respectively.
In this paper, we show improvement in both of these universal relations by restricting to EoSs sampled from GW170817s posterior on pressure as a function of density.
%%%%%%%%%%%%%%%%%%%%%%%%% Begin universal relations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Universal relations}\label{sec:universal}
In this section, we follow the analyses performed in~\cite{Yagi:binLove,Yagi:ILQ} with two new sets of 100 spectrally generated EoS: (i) posterior samples randomly selected from GW170817s 90\% posterior on on pressure as a function of density as shown in the left panel of Fig.~\ref{fig:eos}, and (ii) those unconstrained by any prior EoS information, as shown in the right panel of Fig.~\ref{fig:eos}.\kc{only one panel}

@@

\begin{table}
\centering
\caption{
Comparison between the universal relations (I-Love-Q, C-Love, and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here. 
The maximum EoS variation, given by the largest fractional difference from the fits as shown in Figs.~\ref{fig:ILQ} and~\ref{fig:binLove}, sees a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as previous works.
Additionally, notice how the maximal EoS variation for the unconstrained set of EoSs is slightly higher than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.
}\label{tab:maxVar}
\begin{tabular}{ c  || c c c } 
 \hline
 \hline
 \textbf{Universal} & \multicolumn{3}{c}{\textbf{Maximal EoS Variability}} \\
 \cline{2-4}
 \textbf{Relation} & \multicolumn{1}{c|}{\emph{Previous}} & \multicolumn{1}{c|}{\emph{Unconstrained}} & \emph{Constrained}\\
 \hline
 $\bar{I}-\Lambda$ &  $0.0059$ & $0.0076725$ & $0.0031383$\\
 $\bar{Q}-\Lambda$ & $0.010$ & $0.012617$ & $0.0046612$\\
 $\bar{I}-\bar{Q}$ & $0.012$ & $0.014895$ & $0.0057157$\\
 \hline
 $\bar{C}-\Lambda$ & $0.065$ & $0.071975$ & $0.021688$\\
 \hline
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.50$} & \multirow{2}{*}{$0.5723891$} & \multirow{2}{*}{$0.2140192$}\\
 $(q=0.90)$ & & &\\
 \cline{1-1}
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.20$} & \multirow{2}{*}{$0.2447418$} & \multirow{2}{*}{$0.0828446$}\\
  $(q=0.7)$ & & &\\
  \cline{1-1}
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.025$} & \multirow{2}{*}{$0.0384088$} & \multirow{2}{*}{$0.0182308$}\\
  $(q=0.50)$ & & &\\
  \cline{1-1}
\hline
\hline
\end{tabular}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%% Begin Discussion %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Discussion}\label{sec:conclusion}
The recent GW observation of binary NS merger GW170817 placed constraints on the supranuclear matter EoS for NSs.
We take advantage of this by generating a restricted set of spectral EoSs which agree with this observation to reduce uncertainties upon the extraction of tidal parameters from future GW events.
Important previous work by Yagi and Yunes~\cite{Yagi:ILQ,Yagi:binLove} found EoS-insensitive universal relations between symmetric and antisymmetric combinations of NS tidal deformabilities, which aid in the extraction of said tidal parameters.
We find an improvement upon these universal relations by a factor of $\sim 59$\% for stars with mass ratios of $0.75$ by restricting to the EoS posterior samples from GW170817s 90\% credible region on pressure as a function of density.
Similarly, we find an increase in C-Love and I-Love-Q universality by a factors of $\sim 76$\% and $\sim 50$\%, respectively.
Additionally, we find that hybrid quark-hadron star EoSs \emph{do} obey the I-Love-Q and C-Love universality, albeit with a slightly higher maximum EoS variability as displayed in Tabs.~\ref{tab:hybridCompare} and ~\ref{tab:hybridCompareClove}.
In addition, we find that binaries consisting of one massive hybrid quark-hadron star, and one small-mass hadron star do not obey the binary Love universal relations -- explained by the large difference in $\tilde{\Lambda}$ displayed between the constituent stars.
To improve on this, we construct new ``hybrid matter binary Love relations", applied to only the hybrid branches of the transitional EoSs.
This results in EoS variability similar to that found for the nuclear matter fits.
Further, we analyze the impact of this improvement for future binary NS merger detections, as the current detector sensitivity is not yet small enough to accurately constrain $\tilde{\Lambda}$ enough for universal relations to make a difference.
We find that future interferometers Voyager, CE, and ET-D all experience statistical uncertainties upon the extraction of $\tilde{\Lambda}$ small enough to become comparable to the systematic errors injected through the use of improved universal relations (found to be $12.014$), as depicted in Fig.~\ref{fig:stackedFisher} and Table~\ref{tab:variances}.
Finally, in Appendix~\ref{app:measurement} we investigate the effect of NS binary mass ratio q on the measurement accuracy of $\tilde\Lambda$.
We find that second generation interferometers lose accuracy as one increases the mass ratio, while third generation detectors observe a large increase of accuracy due to the correlations between $\tilde\Lambda$ and $\delta\tilde\Lambda$.
This indicates that the use and further improvement of universal relations is justified for future GW observations of binary NS merger events.
